Oral contraceptives

### 2020-12-16 r_notebooks/exploring_oral_anticoagulants.Rmd

```{r, health-board-modelling}
# system.time(oac_hb_cv_models <-
#   regionalCV(data = oac_monthly_quantity_hb_pre_cv19))
# 
# oac_hb_cv_models %>%
#   write_rds("../data/oac_hb_cv_models.rds")

@@

* 724.044 seconds with multisession prophetModels()

```{r}
# system.time(oac_hb_fcsts <- regionalJointFcsts(oac_monthly_quantity_hb_pre_cv19))
# 
# oac_hb_fcsts %>%
#   write_rds("../data/oac_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling}
# system.time(oac_gp_cluster_cv_models <-
#   regionalCV(data = oac_monthly_quantity_cluster_pre_cv19))
# 
# oac_gp_cluster_cv_models %>%
#   write_rds("../data/oac_gp_cluster_cv_models.rds")

@@

```{r}
# system.time(oac_gp_cluster_fcsts <- regionalJointFcsts(oac_monthly_quantity_cluster_pre_cv19))
# 
# oac_gp_cluster_fcsts %>%
#   write_rds("../data/oac_gp_cluster_fcsts.rds")

@@

# system.time(oac_gp_cv_models <-
#   oac_monthly_quantity_gp_pre_cv19 %>%
#     filter(!regional_unit %in% incomplete_gp) %>%
#               regionalCV())
# 
# oac_gp_cv_models %>%
#   write_rds("../data/oac_gp_cv_models.rds")

@@

```{r}
system.time(oac_gp_fcsts <-
              oac_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% incomplete_gp) %>%
              regionalJointFcsts())
oac_gp_fcsts %>%
  write_rds("../data/oac_gp_fcsts_1.rds")

oac_gp_cluster_fcsts <- 
  read_rds("../data/oac_gp_fcsts_1.rds")
```

@@

best_model_hb %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_hb_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_hb, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

@@

best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_gp_cluster_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  # scale_color_gradientn(colours = rainbow(100))+
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

```{r}
library(tidyLPA)
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_gp_cluster_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
    select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
    estimate_profiles(1:5,
                      variances = c("equal", "varying"),
                      covariances = c("zero", "varying")
                      ) %>% 
    compare_solutions(statistics = c("AIC", "BIC"))
```

>>>>

```{r, health-board-modelling}
plan(multisession)
system.time(oac_hb_cv_models <-
  regionalCV(data = oac_monthly_quantity_hb_pre_cv19))
plan(sequential)

oac_hb_cv_models %>%
  write_rds("../data/oac_hb_cv_models.rds")

@@

* 476.383 seconds 2020-12-13

```{r}
system.time(oac_hb_fcsts <- regionalJointFcsts(oac_monthly_quantity_hb_pre_cv19))

oac_hb_fcsts %>%
  write_rds("../data/oac_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling}
plan(multisession)
system.time(oac_gp_cluster_cv_models <-
  regionalCV(data = oac_monthly_quantity_cluster_pre_cv19))
plan(sequential)

oac_gp_cluster_cv_models %>%
  write_rds("../data/oac_gp_cluster_cv_models.rds")

@@

```{r}
system.time(oac_gp_cluster_fcsts <- regionalJointFcsts(oac_monthly_quantity_cluster_pre_cv19))

oac_gp_cluster_fcsts %>%
  write_rds("../data/oac_gp_cluster_fcsts.rds")

@@

system.time(oac_gp_cv_models <-
  oac_monthly_quantity_gp_pre_cv19 %>%
    filter(!regional_unit %in% incomplete_gp) %>%
              regionalCV())

oac_gp_cv_models %>%
  write_rds("../data/oac_gp_cv_models.rds")

@@

```{r}
# plan(multisession)
# system.time(oac_gp_fcsts <-
#               oac_monthly_quantity_gp_pre_cv19 %>%
#               filter(!regional_unit %in% incomplete_gp) %>%
#               regionalJointFcsts())
# plan(sequential)
# oac_gp_fcsts %>%
#   write_rds("../data/oac_gp_fcsts_1.rds")

oac_gp_fcsts <-
  read_rds("../data/oac_gp_fcsts_1.rds")

* 2781.052 seconds

@@

best_model_hb %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_hb_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_hb, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

@@

best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  # scale_color_gradientn(colours = rainbow(100))+
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

```{r, eval = FALSE}
library(tidyLPA)
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oac_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oac_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
    select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
    estimate_profiles(1:5,
                      variances = c("equal", "varying"),
                      covariances = c("zero", "varying")
                      ) %>% 
    compare_solutions(statistics = c("AIC", "BIC"))
```

### 2020-12-16 r_notebooks/exploring_oral_contraceptives.Rmd

```{r setup}
## Packages
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)
options(future.rng.onMisue = "ignore")

@@

## Functions
source("../r_scripts/functions.r")

## Drugs of interest
combined_hormonal <- 
  c("0703010E0", "0703010F0", "0703010G0", "0703010H0", "0703010M0",
    "0703010S0", "0703010R0","0703010A0", "0703010P0")
progestogen_only <- 
  c("0703021Q0", "0703022P0", "0703021C0", "0703021L0", "0703023L0",
    "0703022M0", "0703021N0", "0703022N0", "0703021P0")

@@

```{r}
# system.time(oc_hb_fcsts <- regionalJointFcsts(oc_monthly_quantity_hb_pre_cv19))
# 
# oc_hb_fcsts %>% 
#   write_rds("../data/oc_hb_fcsts.rds")

@@

```{r}
# system.time(oc_gp_cluster_fcsts <- regionalJointFcsts(oc_monthly_quantity_cluster_pre_cv19))
# 
# oc_gp_cluster_fcsts %>%
#   write_rds("../data/oc_gp_cluster_fcsts.rds")

@@

```{r}
# system.time(oc_gp_fcsts <- 
#               oc_monthly_quantity_gp_pre_cv19 %>% 
#               filter(!regional_unit %in% incomplete_gp) %>% 
#               regionalJointFcsts())
# oc_gp_fcsts %>% 
#   write_rds("../data/oc_gp_fcsts.rds")

oc_gp_cluster_fcsts <- 
  read_rds("../data/oc_gp_fcsts.rds")
```

@@

best_model_hb %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_hb_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_hb, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none") #+
  facet_wrap(~.model)
```

@@

best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  scale_color_gradientn(colours = rainbow(100))+
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

```{r}
library(tidyLPA)
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
    select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
    estimate_profiles(1:5,
                      variances = c("equal", "varying"),
                      covariances = c("zero", "varying")
                      ) %>% 
    compare_solutions(statistics = c("AIC", "BIC"))
```

@@

best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

## Plotting

```{r}
best_model <- 
  oc_gp_cluster_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcsts$forecasts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  ggplot(aes(x = datename)) +
  geom_line(aes(y = .mean, colour = as.factor(regional_unit))) +
  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, fill = as.factor(regional_unit),
              alpha = .05), outline.type = "both") +
  geom_line(aes(y = n, group = regional_unit, colour = as.factor(regional_unit)), lty = 3) +
  coord_cartesian(ylim = c(0,50))+
  theme(legend.position = "none") +
  facet_wrap(~.model) + 
  labs(caption = "Dotted line = observed data, solid line and ribbon is predicted data with 80% CIs")

```{r}
bestModelPlot <- function(models, forecasts, data, region){
  best_model <- 
    models %>% 
    group_by(regional_unit) %>% 
    arrange(RMSE, MAE) %>% 
    slice(1, .preserve = TRUE)

  full_data <- filter(data, 
                      datename > ymd("2020-02-28") &
                        regional_unit == region) %>% 
    mutate(datename = yearmonth(datename))

best_model %>% 
    select(.model, regional_unit) %>% 
    filter(regional_unit == region) %>% 
    inner_join(forecasts, by = c(".model", "regional_unit")) %>%
    left_join(full_data, by = c("datename", "regional_unit")) %>% 
    ggplot(aes(x = datename, colour = as.factor(regional_unit))) +
    geom_line(aes(y = .mean)) +
    geom_ribbon(aes(ymin = lb_80, ymax = ub_80, fill = as.factor(regional_unit),
                   alpha = .1)) +
    geom_line(aes(y = n),
              colour = "black") +
    theme(legend.position = "none") +
    facet_wrap(~.model)
}

bestModelPlot(models = oc_gp_cluster_cv_models, 
              forecasts = oc_gp_cluster_fcsts$forecasts,
              data = oc_monthly_quantity_cluster,
              region = "CityHealth")

>>>>

```{r setup}
## Packages
# devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(serCymruTools)

## Options
knitr::opts_chunk$set(cache = TRUE)
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

@@

```{r}
## Drugs of interest
combined_hormonal <- 
  c("0703010E0", "0703010F0", "0703010G0", "0703010H0", "0703010M0",
    "0703010S0", "0703010R0","0703010A0", "0703010P0")
progestogen_only <- 
  c("0703021Q0", "0703022P0", "0703021C0", "0703021L0", "0703023L0",
    "0703022M0", "0703021N0", "0703022N0", "0703021P0")

@@

```{r}
# plan(multisession)
# system.time(oc_hb_fcsts <- regionalJointFcsts(oc_monthly_quantity_hb_pre_cv19))
# plan(sequential)
# 
# oc_hb_fcsts %>%
#   write_rds("../data/oc_hb_fcsts.rds")

@@

```{r}
# plan(multisession)
# system.time(oc_gp_cluster_fcsts <- regionalJointFcsts(oc_monthly_quantity_cluster_pre_cv19))
# plan(sequential)
# 
# oc_gp_cluster_fcsts %>%
#   write_rds("../data/oc_gp_cluster_fcsts.rds")

@@

```{r}
# plan(multisession)
# system.time(oc_gp_fcsts <-
#               oc_monthly_quantity_gp_pre_cv19 %>%
#               filter(!regional_unit %in% incomplete_gp) %>%
#               regionalJointFcsts())
# plan(sequential)
# oc_gp_fcsts %>%
#   write_rds("../data/oc_gp_fcsts.rds")

oc_gp_fcsts <- 
  read_rds("../data/oc_gp_fcsts.rds")
```

@@

best_model_hb %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_hb_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_hb, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none") #+
  facet_wrap(~.model)
```

@@

best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  # scale_color_gradientn(colours = rainbow(100))+
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```

```{r}
library(tidyLPA)
best_model_gp_cluster %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_cluster_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_cluster, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd)  %>%
    select(discrepancy, regional_unit, datename) %>%
  pivot_wider(names_from = datename, values_from = discrepancy) %>% 
  ungroup() %>% 
  select(-regional_unit) %>% 
  # estimate_profiles(n_profiles = 4, models = 1) %>% plot_profiles()
    estimate_profiles(1:5,
                      variances = c("equal", "varying"),
                      covariances = c("zero", "varying")
                      ) %>% 
    compare_solutions(statistics = c("AIC", "BIC"))
```

@@

best_model_gp %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(oc_gp_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(oc_monthly_quantity_gp, 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - .mean,
         z_discrepancy = discrepancy/sd) %>% 
  ggplot(aes(y = discrepancy)) +
  # geom_boxplot(aes(x = as.factor(datename))) +
  geom_line(aes(x = datename, y = discrepancy, colour = as.factor(regional_unit)),
            alpha = .8, lty = 2) +
  geom_hline(aes(yintercept = 0), colour = "red") +
  theme(legend.position = "none")
```
